\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.8in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome5} % for icons
\pagestyle{empty}

\begin{document}

% Header block
\noindent
\begin{minipage}[t]{0.55\textwidth}
    {\Large\bfseries SHAIK ASIF}\\[2pt]
   \\[0.2em] B.Tech in Cyber Security Engineering\\
    Sphoorthy Engineering College, Hyderabad
\end{minipage}
\hfill
\begin{minipage}[t]{0.4\textwidth}
    \raggedleft
    \faPhone*\ \ +91-8247702576\\
    \faEnvelope\ \href{mailto:phenominalasif@gmail.com}{phenominalasif@gmail.com} \\
    \faGithub\ \ \href{https://github.com/your-github}{https://github.com/ShaikAsif001}\\
    \faLinkedin\ \ \href{https://www.linkedin.com/in/shaik-asif-ab1a58202}{linkedin.com/in/shaik-asif-ab1a58202}
\end{minipage}



% Summary
\section*{Professional Summary}
\vspace{-1.5em}% adjust if needed
\rule{\textwidth}{0.4pt}


\setlength{\parindent}{0pt}Cybersecurity Engineer with hands-on experience in cyber-crime investigation, incident response, OSINT, threat analysis, and vulnerability assessment. Skilled in analyzing attacker TTPs, monitoring logs using SIEM, mitigating phishing and malware attacks, and strengthening security posture. Passionate about SOC operations, responsible disclosure, and continuous learning in cybersecurity.

% Education
\section*{Education}
\vspace{-1.5em}% adjust if needed
\rule{\textwidth}{0.4pt}
\textbf{Sphoorthy Engineering College, Hyderabad} \hfill 2024\\
B.Tech in Cyber Security Engineering \hfill CGPA: 74\%\\
\\
\textbf{Quli Qutub Shah Polytechnic, Hyderabad} \hfill 2021\\
Diploma in Electrical and Electronics Engineering \hfill CGPA: 75\%\\
\\
\textbf{Royal Mission High School, Hyderabad} \hfill 2018\\
SSC \hfill CGPA: 77\%\\

% EXPERIENCE
\section*{Experience}
\vspace{-1.3em}
\rule{\textwidth}{0.4pt}

% The Tech Unique Academy
\textbf{The Tech Unique Academy} \hfill \textbf{Remote, India $\rightarrow$ 05/2025 -- 10/2025}\\
\textit{Penetration Testing $\star$ Internship}\\[-0.2em]
\begin{itemize}
   \vspace{-1.2em} \item \textbf{Hands-on Practice:} Built labs with Kali Linux/Metasploitable and used platforms like Hack The Box, TryHackMe, and CTFs to develop practical pentesting skills.
    \item \textbf{Foundational Knowledge \& Skills:} Strengthened networking, Linux/Windows internals, scripting (Python/Bash), and core security concepts such as the OWASP Top 10 and common vulnerabilities.
    \item \textbf{Tools \& Techniques:} Worked with Nmap, Burp Suite, Metasploit, Wireshark, and related tools for reconnaissance, scanning, and exploitation.
\end{itemize}

\vspace{0.2em}
% Cyber Crime Investigator + Ethical Hacker
\textbf{Cyber Crime Investigator + Ethical Hacker (Intern)} \hfill \textbf{Remote, India $\rightarrow$ 07/2024 -- 03/2025}\\
\textit{Digital Forensics and Incident Response Intern $\star$ Internship}\\[-0.2em]

\begin{itemize}
    \vspace{-1.2em}\item \textbf{Foundational Knowledge:} Learned digital forensics, network security, malware analysis, and cyber laws relevant to investigations.
    \item \textbf{Hands-on Practice:} Used tools like Autopsy, FTK Imager, EnCase, and Wireshark in lab and virtual environments.
    \item \textbf{Analytical \& Reporting Skills:} Analyzed logs, traced cyberattacks, and documented findings in clear reports for technical or legal use.
\end{itemize}

\vspace{0.2em}
% Sphoorthy Engineering College – Team Captain
\textbf{Sphoorthy Engineering College (Team Captain)} \hfill \textbf{Rangareddy, India $\rightarrow$ 01/2023 -- 06/2024}\\[-0.2em]
\begin{itemize}
    \vspace{-1.2em}\item Spearheaded design and delivery of location tracing and honeypot solutions for academic security projects.
    \item Secured and analyzed utility asset maps to support detailed case-based cyber investigations.
    \item Participated in regular mentor meetings that refined tools and techniques, improving vulnerability assessment accuracy.
\end{itemize}

\vspace{0.2em}
% Cisco Networking Academy
\textbf{Cisco Networking Academy} \hfill \textbf{Remote, India $\rightarrow$ 06/2022 -- 08/2022}\\
\textit{Networking Virtual Internship}\\[-0.2em]
\begin{itemize}
   \vspace{-1.2em} \item Analyzed networking protocols to understand their impact on data transfer efficiency and security using Cisco Packet Tracer.
    \item Enhanced network security awareness by examining protocol weaknesses and recommending security improvements.
    \item Executed simulations to measure the impact of different protocols, contributing to a 15\% improvement in data transfer reliability.
\end{itemize}


% Technical Skills
\section*{Technical Skills}
\vspace{-1.3em}
\rule{\textwidth}{0.4pt}
\vspace{0.3em}\textbf{Cybersecurity:} SIEM Monitoring, Vulnerability Assessment, Incident Response, OSINT, Threat Analysis, Network Security, Malware \& Ransomware Mitigation, Social Engineering Defense \vspace{0.3em}\\ 
\vspace{0.4em}\textbf{Tools:} Kali Linux, Wireshark, Burp Suite, OSINT Tools, SIEM Tools, Virtualization Tools\\
\vspace{0.4em}\textbf{Scripting:} Python (Basics), Bash (Basics)\\
\vspace{0.4em}\textbf{Soft Skills:} Problem Solving, Attention to Detail, Teamwork, Communication
\vspace{-0.5em}

\vspace{-0.2em}
\section*{Projects}
\vspace{-1.3em}
\rule{\textwidth}{0.4pt}
\textbf{OSINT \& Doxing Investigations} \hfill 2025
\begin{itemize}
    \vspace{-0.4em} \item Conducted OSINT-based investigations using Google, Twitter (X), Meta, and other tools.
\end{itemize}

\vspace{-0.3em} \textbf{Honeypot Deployment} \hfill 2024
\begin{itemize}
   \vspace{-0.4em} \item Implemented a honeypot server to capture attacker activities and monitor suspicious traffic.
\end{itemize}

\vspace{-0.3em} \textbf{Keylogger Tracking System} \hfill 2023
\begin{itemize}
    \vspace{-0.4em}\item Designed a detection system to identify unauthorized keystroke logging.
\end{itemize}

\vspace{-0.3em} \textbf{Location Tracking System} \hfill 2023
\begin{itemize}
    \vspace{-0.4em}\item Developed an OSINT-driven location tracing system for cybercrime cases.
\end{itemize}

% Certifications
\section*{Certifications}
\vspace{-1.3em}
\rule{\textwidth}{0.4pt}
\begin{itemize}

    \item Pentration Testing (4 Months)
    \item Cyber Crime Investigation \& Digital Forensics (8 Months)
    \item Cybersecurity professional + Ethical Hacking (10 Months)
    \item Red Teaming Training – Deepcyctes
    \item Ministry of Electronics \& IT – Cybersecurity Certificates
    \item NSIC – EEE (6 Months)
\end{itemize}

% Extra-Curricular
\section*{Additional Strengths}
\vspace{-1.3em}
\rule{\textwidth}{0.4pt}
\begin{itemize}
    \item Quick learner with strong analytical skills.
    \item Works well under pressure and in team environments.
    \item Passionate about bug bounty, SOC operations, and threat hunting.
\end{itemize}

\end{document}
